\Large \bf Lissy: Experimenting with on-chain order books

### 2021-09-10 LaTeX-LNCS-2022/sections/appendix.tex
more changes

\subsection{Ethereum and Blockchain Technology}

@@

\paragraph{Ethereum's Gas Model.}

@@

\paragraph{Gas Refunds.}

@@

@@

\subsection{Optimistic Roll-Ups}
\label{app:rollup}

We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks. However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, roll-up architectures like Loopring, and commit-chain solutions like TEX). We consider an alternative design that is almost as difficult to regulate as a fully on-chain solution. In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders. Traders still only interact with Ethereum.

\section{Cleaning Up Revisited: Clearing Mappings}
\label{app:clean}

>>>>

\subsection{Ethereum and Blockchain Technology}
\label{app:ethback}

@@

\subsubsection{Ethereum's Gas Model.}

@@

\subsubsection{Gas Refunds.}

@@

\subsubsection{Optimistic Roll-Ups.}
\label{app:rollup}

%We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks. However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, roll-up architectures like Loopring, and commit-chain solutions like TEX). We consider an alternative design that is almost as difficult to regulate as a fully on-chain solution. In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders. Traders still only interact with Ethereum.

\subsubsection{Arbitrum}

Arbitrum is an Ethereum Layer 2 scaling solution that operates as an optimistic roll-up~\cite{kalodner2018arbitrum}. Arbitrum runs entire DApps inside its environment, which acts like a container and requires special bridge contacts to interact with `normal' (or Layer 1) Ethereum DApps. To deploy a DApp on Arbitrum, or to execute a function on an existing Arbitrum DApp, the transaction is sent to an \textit{Inbox contract} on Layer 1. The transaction is not executed, it is only recorded (as calldata) in the Inbox. Like any other transactions on Ethereum, miners determine the order of the transactions sent to this contract. A set of validators (open to anyone) are watching the Inbox contract for new transactions. Once an Inbox transaction is finalized in an Ethereum block, validators will execute the transaction and assert the result of the execution to other validators on a sidechain called ArbOS. Once the dispute challenge period is over, the new state of ArbOS will be inserted into Ethereum. As the Inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not performed correctly. Disputes are adjudicated by Ethereum itself and require essentially constant gas costs, regardless of the size of the gas costs of the transaction being disputed

@@

\section{Cleaning-Up Revisited: Clearing Mappings}
\label{app:clean}

### 2021-09-10 LaTeX-LNCS-2022/sections/paper.tex
more changes

We assume the reader is familiar with the following concepts: blockchain technology; smart contracts and decentralized applications (DApps) on Ethereum; how Ethereum transactions are structured, broadcasted, and finalized; the gas model including the gas limit (approximately 11M gwei at the time of our experiments) per block. A \textbf{gas refund} is a more esoteric subject (not covered thoroughly in any academic work to our knowledge) that we use heavily in our optimizations. Briefly, certain EVM operations (\texttt{SELFDESTRUCT} and \texttt{SSTORE 0}) cost negative gas, with the follow caveats: the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with an 11M limit). We provide full details of all of these topics in Appendix~\ref{app:back}.

@@

\paragraph{Refunds and PQs.}

@@

Dequeuing in a linked list with mapping can be implemented in two ways. The simplest approach is to process a node, update the head pointer, and leave the `removed' node's data behind in the mapping untouched (where it will never be referenced again). Alternatively, we can call \texttt{DELETE} on each mapping entry once we finish processing a node in the PQ. As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on the blockchain is cheaper than cleaning it up.

The lesson here is that gas refunds incentivize developers to clean up storage variables they will not use again, but it is highly contextual as to whether it will pay for itself. Further, the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction). This is a complicated and under-explored area of Ethereum in the research literature. For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup.

@@

The main research question is how many orders can be processed in a single Ethereum transaction when closing the call market. The choice of PQ implementation is the main influence on performance and the results are shown in Table~\ref{tab:worst_case_matching}. These numbers are for the \textit{worst-case}---when every submitted bid and ask is marketable (\ie will require fulfillment). In practice, once \texttt{closeMarket()} hits the first bid or ask that cannot be executed, it can stop processing all remaining orders. Premised on Ethereum becoming more efficient over time, we were interested in how much gas it would cost to execute 1000 pairs of orders, which is given in the third column. The fourth column indicates the cost of submitting a bid or ask --- since this cost will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.

% We implemented a generic call market that interfaces with a generic PQ (at its own contract address) and ran experiments for each PQ implementation. We looked at . Table~\ref{tab:worst_case_matching} shows the performance results of \cm for each PQ variant. In the first two columns, we determine the highest number of trades that can be executed and processed in a single call to the \texttt{closeMarket()} and not exceed the current Ethereum block gas limit of 11,741,495. Since Ethereum will become more efficient over time, we were also interested in how much gas it would cost to execute 1000 pairs of orders, which is given in the third column. The fourth column indicates the cost of submitting a bid or ask --- since this cost will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.

As expected, the numbers closely track the performance of the PQ itself, suggesting the PQ is indeed the main influence on performance. In Ethereum today, call markets appear to be limited to processing about a hundred orders per transaction. If markets open on every other block and the call market could monopolize an entire block to close, a few hundred orders per minute (worst-case) can be processed. The main takeaway is that the transparency, front-running resistance, and low barrier to entry of Ethereum come with an enormous cost (\ie an institutional exchange like NASDAQ can process 100K trades per second). That said, many exchanges trade the same assets under different trading rules (\ie market fragmentation) because traders have different preferences. \cm can work today in some circumstances like very low liquidity tokens, or markets with high volumes and a small number of traders (\eg liquidation auctions).

%\textblue{Notes on Front-running Table:}
%\begin{itemize}
%\item{Mallory squeezes her order before Alice's.} Mallory sees that there is an incoming bid at 200 for 10 of an asset, and currently, the best offer is at 190 for the same volume. In this case, Mallory sends her bid at 190 for 10 and immediately inserts the sell order at 200. If Alice's transaction gets executed, Mallory will profit on the price difference.
%\textblue{Sandwich Attacks:} These attacks apply to automated market makers (\ie UniSwap) and exploit a particular feature of AMMs, which is for every swap that takes place on an AMM, the price of the token being swapped shifts slightly. In this case, if Mallory realizes that there is an incoming trade of asset A for asset B, She immediately inserts a bid for asset B. This transaction will increase the price of asset B significantly and when Alice's transaction gets executed on the AMM, she'll receive less number of asset B as she is purchasing it at an inflated price. Right after Alice's transaction goes through, Mallory will sell the amount of asset B she has bought at a higher price.
%\end{itemize}

%\input{tables/frontrunning.tex}
\input{tables/frontrunning2.tex}

Some attacks combine more than one insertion, displacement, and/or suppression attacks. AMMs are vulnerable to a double insertion called a sandwich attack~\cite{ZQFLG21} which bookends a victim's trade with the front-runner's trades (plus additional variants). In a traditional call market, a market clearing price is chosen and all trades are executed at this price. All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a \textit{price improvement} and it allows traders to submit at their best price. A hybrid front-running attack allows Mallory to extract any price improvements. Consider the case where Alice's ask crosses Bob's bid with a material price improvement. Mallory inserts a bid at Alice's price, suppresses Bob's bid until the next call, and places an ask at Bob's price. She buys and then immediately sells the asset and nets the price improvement as arbitrage. To mitigate this in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()})\textblue{traders would have to pay for that}. This does not actively hurt traders---they always receive the same price that they quote in their orders---and it removes any incentive for miners to front-run these profits.

Other front-running attacks use order cancellations (discussed in the next section) which \cm mitigates by running short-lived markets with no cancellations.

There are two main takeaways from Table~\ref{tab:front}. Call markets provide strong resilience to front-running only bested slightly by dark markets like TEX~\cite{khalil2019tex}, however they do it through design---no cryptography and no two-round protocols. A second observation is that dark call markets, like Galal \etal~\cite{galalpublicly}, are no more resilient to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that are reactionary but do not front-run).

@@

@@

>>>>

We assume the reader is familiar with the following concepts: blockchain technology; smart contracts and decentralized applications (DApps) on Ethereum; how Ethereum transactions are structured, broadcasted, and finalized; the gas model including the gas limit (approximately 11M gwei at the time of our experiments) per block. A \textbf{gas refund} is a more esoteric subject (not covered thoroughly in any academic work to our knowledge) that we use heavily in our optimizations. Briefly, certain EVM operations (\texttt{SELFDESTRUCT} and \texttt{SSTORE 0}) cost negative gas, with the follow caveats: the refund is capped at 50\% of the total gas cost of the transaction, and (2) the block gas limit applies to the pre-refunded amount (\ie a transaction receiving a full refund can cost up to 5.5M gas with an 11M limit). We provide full details of all of these topics in Appendix~\ref{app:ethback}.

@@

@@

Dequeuing in a linked list with mapping can be implemented in two ways. The simplest approach is to process a node, update the head pointer, and leave the `removed' node's data behind in the mapping untouched (where it will never be referenced again). Alternatively, we can call \texttt{DELETE} on each mapping entry once we finish processing a trade. As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on the blockchain is cheaper than cleaning it up.

The lesson here is that gas refunds incentivize developers to clean up storage variables they will not use again, but it is highly contextual as to whether it will pay for itself. Further, the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction).  In Appendix~\ref{app:clean}, we present a second case study of the cost-benefits of clearing a mapping when it is no longer needed (including our idea to store the mapping in its own contract so it can \texttt{SELFDESTRUCT} with a single function call). The unfortunate takeaway is, again, that it is cheapest to leave the mapping in place. Cleaning up EVM state is a complicated and under-explored area of Ethereum in the research literature. For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup.

@@

The main research question is how many orders can be processed under the Ethereum block gas limit. The choice of PQ implementation is the main influence on performance and the results are shown in Table~\ref{tab:worst_case_matching}. These numbers are for the \textit{worst-case}---when every submitted bid and ask is marketable (\ie will require fulfillment). In practice, once \texttt{closeMarket()} hits the first bid or ask that cannot be executed, it can stop processing all remaining orders. Premised on Ethereum becoming more efficient over time, we were interested in how much gas it would cost to execute 1000 pairs of orders, which is given in the third column. The fourth column indicates the cost of submitting a bid or ask --- since this cost will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.

The main takeaway is that call markets appear to be limited to processing about a hundred orders per transaction and even that is at the enormous cost of monopolizing an entire Ethereum block just to close the market. Perhaps \cm can work today in some circumstances like very low liquidity tokens, or markets with high volumes and a small number of traders (\eg liquidation auctions).

@@

We consider an alternative design for \cm that is almost as difficult to regulate as a fully on-chain solution. In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders. Traders still only interact with Ethereum.

@@

\input{tables/frontrunning2.tex}

Some attacks combine more than one insertion, displacement, and/or suppression attacks. AMMs are vulnerable to a double insertion called a sandwich attack~\cite{ZQFLG21} which bookends a victim's trade with the front-runner's trades (plus additional variants). In a traditional call market, a market clearing price is chosen and all trades are executed at this price. All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a \textit{price improvement} and it allows traders to submit at their best price. A hybrid front-running attack allows Mallory to extract any price improvements. Consider the case where Alice's ask crosses Bob's bid with a material price improvement. Mallory inserts a bid at Alice's price, suppresses Bob's bid until the next call, and places an ask at Bob's price. She buys and then immediately sells the asset and nets the price improvement as arbitrage. To mitigate this in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}). This does not actively hurt traders---they always receive the same price that they quote in their orders---and it removes any incentive for miners to front-run these profits.

Other front-running attacks use order cancellations (see Section~\ref{sec:cancel}) which \cm mitigates by running short-lived markets with no cancellations.

There are two main takeaways from Table~\ref{tab:front}. Call markets provide strong resilience to front-running only bested slightly by dark markets like TEX~\cite{khalil2019tex}, however they do it through design---no cryptography and no two-round protocols. A second observation is that dark call markets, like Galal \etal~\cite{galalpublicly}, are no more resilient to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that react quickly to trades without acutally front-running).

% = = = = =
